Illustration: Feature Based Time Series Clustering in Psychology [tsFeatureClustR]

### 2024-11-13 tutorial/06-validation-analyses.qmd
de-anonymized for publication

<div class="d-flex justify-content-center">
  <a class="btn btn-primary btn-lg" href="https://jannis-kreienkamp.shinyapps.io/tsFeatureClustR/" target="_blank" role="button">To the Web App</a>
</div>

>>>>

<div class="d-flex justify-content-center">
  <a class="btn btn-primary btn-lg" href="https://tsfeatureclustr.shinyapps.io/webapp/" target="_blank" role="button">To the Web App</a>
</div>

### 2024-11-13 tutorial/about.qmd
de-anonymized for publication

We provide all data necessary to replicate the full results of the main manuscript as well as this illustration. We specifically provide a minial reproducible dataset that includes all variables necessary to perform the analysis, while still protecting the privacy and confidentiality of the participants. All data is available as part of [our Open Science ](https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4) [@KreienkampMasked-clust-osf].

@@

The full code of this illustration as well as the main manuscript is available as part of [our GitHub repository](https://github.com) [@KreienkampMasked-clust-github]. A minimal version of the code as well as an archive file are available in [our Open Science ](https://osf.io/75ryj/?view_only=db14031cd8704085b5c6165c9f5ed3e4) [@KreienkampMasked-clust-osf]. For convenience purposes, we have also collected a number of functions we created as part of the illustration as an R-package. This package is available as its own GitHub repository and can be downloaded with the `devtools` package `devtools::install_github("JannisCodes/tsFeatureExtracR")`, you can also [download the R package here](https://github.com/JannisCodes/tsFeatureExtracR/archive/refs/tags/v.0.1.0.tar.gz) [@KreienkampBlinded2023-tsFeatureExtracR].

>>>>

We provide all data necessary to replicate the full results of the main manuscript as well as this illustration. We specifically provide a minial reproducible dataset that includes all variables necessary to perform the analysis, while still protecting the privacy and confidentiality of the participants. All data is available as part of [our Open Science repository](https://doi.org/10.17605/OSF.IO/J8DZV) [@Kreienkamp-clust-osf].

@@

The full code of this illustration as well as the main manuscript is available as part of [our GitHub repository](https://github.com/JannisCodes/migration-trajectories) [@Kreienkamp-clust-github]. A minimal version of the code as well as an archive file are available in [our Open Science repository](https://doi.org/10.17605/OSF.IO/J8DZV) [@Kreienkamp-clust-osf]. For convenience purposes, we have also collected a number of functions we created as part of the illustration as an R-package. This package is available as its own GitHub repository and can be downloaded with the `devtools` package `devtools::install_github("JannisCodes/tsFeatureExtracR")`, you can also [download the R package here](https://tsfeatureclustr.com/assets/tsFeatureExtracR_0.1.0.tar.gz) [@Kreienkamp2023-tsFeatureExtracR].

### 2024-11-13 tutorial/index.qmd
config updated
de-anonymized for publication

---
title: "Illustration: Feature Based Time Series Clustering in Psychology [tsFeatureExtracR]"
author:
  - name: Jannis Kreienkamp
    orcid: 0000-0002-1831-5604
    email: j.kreienkamp@rug.nl
    corresponding: true
    # affiliations:
    #   - ref: rug
  - name: Maximilian Agostini
    orcid: 0000-0001-6435-7621
    # affiliations:
    #   - ref: rug
  - name: Rei Monden
    orcid: 0000-0003-1744-5447
    # affiliations:
    #   - ref: hu
  - name: Kai Epstude
    orcid: 0000-0001-9817-3847
    # affiliations:
    #   - ref: rug
  - name: Peter de Jonge
    orcid: 0000-0002-0866-6929
    # affiliations:
    #   - ref: rug
    #   - ref: icpe
  - name: Laura F. Bringmann
    orcid: 0000-0002-8091-9935
    # affiliations:
    #   - ref: rug
    #   - ref: icpe
# affiliations:
#   - id: rug
#     name: University of Groningen
#   - id: hu
#     name: Hiroshima University
#   - id: icpe
#     name: ICPE
---

@@

1. [Input variables](01-input-variables.qmd)
2. [Feature extraction](02-feature-extraction.qmd)
3. [Feature reduction](03-feature-reduction.qmd)
4. [Clustering](04-clustering.qmd)
5. [Evaluation](05-evaluation.qmd)
6. [About](about.qmd)

>>>>

---
title: "Illustration: Feature Based Time Series Clustering in Psychology [tsFeatureClustR]"
author:
  # - name: Masked for Peer Review
  # - name: ██████ ██████████
  #   orcid: 0000-0000-0000-0000
  # - name: ██████████ ████████
  #   orcid: 0000-0000-0000-0000
  # - name: ███ ██████
  #   orcid: 0000-0000-0000-0000
  # - name: ███ ███████
  #   orcid: 0000-0000-0000-0000
  # - name: █████ ██ █████
  #   orcid: 0000-0000-0000-0000
  # - name: █████ ██ █████████
  #   orcid: 0000-0000-0000-0000
- name: Jannis Kreienkamp
  orcid: 0000-0002-1831-5604
  email: jannis@thedataflowcompany.com
  corresponding: true
  # affiliations:
  #   - ref: rug
- name: Maximilian Agostini
  orcid: 0000-0001-6435-7621
  # affiliations:
  #   - ref: rug
- name: Rei Monden
  orcid: 0000-0003-1744-5447
  # affiliations:
  #   - ref: hu
- name: Kai Epstude
  orcid: 0000-0001-9817-3847
  # affiliations:
  #   - ref: rug
- name: Peter de Jonge
  orcid: 0000-0002-0866-6929
  # affiliations:
  #   - ref: rug
  #   - ref: icpe
- name: Laura F. Bringmann
  orcid: 0000-0002-8091-9935
  # affiliations:
  #   - ref: rug
  #   - ref: icpe
# affiliations:
#   - id: rug
#     name: University of Groningen
#   - id: hu
#     name: Hiroshima University
#   - id: icpe
#     name: ICPE
---

@@

1. [Input variables](01-input-variables.qmd)
2. [Feature extraction](02-feature-extraction.qmd)
3. [Feature reduction](03-feature-reduction.qmd)
4. [Clustering](04-clustering.qmd)
5. [Evaluation](05-evaluation.qmd)
6. [Validation Analyses](06-validation-analyses.qmd)
7. [About](about.qmd)
